---
title: "Homework 5"
author: "Niva Shirsekar"
date: "2024-10-22"
output:
  html_document:
    toc: true
    toc_float: true
---


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(sas7bdat)
library(rvest)
```

# **Question 1**

```{r}
#Downloading and reading astronauts dataset
astronauts <- read.csv("~/Downloads/R Stuff/astronauts.csv")
ast_ggplot <- ggplot(astronauts)

#Making a boxplot of the mission year variable
ast_ggplot + geom_boxplot(aes(x=Mission.Year), fill="darkgreen", ) + labs(title="Boxplot of Mission Years", x= "Years")
```

EVA stands for extravehicular activity. The two variable names in which this occurs is Mission.Durations.EVA, and Profile.Lifetime Statistics.EVA. These variables describe the extravehicular activity during the duration of the missions and astornaut goes on and the EVA during their entire lifetime. 

# **Question 2**

```{r warning = FALSE}
#downloading and reading scraped olympics dataset (scraped from the Wikipedia website and formatted in Google sheets)
olympics <- read.csv("~/Downloads/R Stuff/Olympics.csv")

#Filling in the missing US total summer gold values
olympics$Summer.Gold[150] =1105

#converting character variables to numeric variables
olympics$Summer.Gold <- as.numeric(as.character(olympics$Summer.Gold))

# Sort the dataset by Summer Gold Medals in descending order
sorted_gold <- olympics[order(-olympics$Summer.Gold), ]
tibble(head(sorted_gold, 10))


#converting character variables to numeric variables
olympics$Summer.Total <- as.numeric(as.character(olympics$Summer.Total))

#Scatterplot comparing total summer medals and total winter meadals 
olymp_ggplot <- ggplot(olympics)
olymp_ggplot + geom_point(aes(x=Summer.Total, y=Winter.Total), color = "coral") + labs(title="Summer vs Winter Total Medals", x = "Summer Total Medals", y = "Winter Total Medals") + 
  theme(axis.text.x = element_text(angle = 50, hjust = 1, size = 12)) +theme(aspect.ratio = 1/2) 

```

# **Question 3**

```{r}
#Scraping the data from the SDS course inventory page 
stats_link <- "https://stat.utexas.edu/academics/undergraduate-course-inventory"
stats_page <- read_html(stats_link)

#scraping course number and title
course_names <- html_text(html_elements(stats_page, ".column-count-2 a"))

#scraping course descriptions
course_descriptions <- html_text(html_elements(stats_page, "h4+ p"))

#creating and printing a tibble
SDS_course_tib = tibble("Course Number/Title" = course_names, "Description" = course_descriptions)
print(SDS_course_tib, n = Inf)
```

# **Question 4**

```{r}
#scraping data from the Harvard Biostatistics PhD student directory
harvard_link <- "https://www.hsph.harvard.edu/biostatistics/phdstudents/"
harvard_page <- read_html(harvard_link)

#scraping student names 
student_name <- html_text(html_elements(harvard_page, "h4"), trim = TRUE)

#scraping student emails
student_email <- html_text(html_elements(harvard_page, "p:nth-child(1) , h5+ p"), trim = TRUE)

#creating and printing the tibble
harvtib = tibble("Student Names" = student_name, "Student Emails" = student_email)
print(harvtib, n = Inf)
```

Gopal Kotecha was missing an email in the directory, so his email is just shown as some of his profile information. Rebecca Danning and Jane Liang also had some of their personal profile information get caught in the webscrape. 


