---
title: "Homework 6"
author: "Niva Shirsekar"
date: "2024-10-30"
output: 
   html_document:
    toc: true
    toc_float: true
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, tidy = TRUE, tidy.opts=list(width.cutoff=60))

```


```{r}
#loading in necessary libraries 
library(tidyverse)
library(dplyr)
library(forcats)
library(lubridate)
library(purrr)
library(stringr)
library(readr)
library(tibble)
library(tidyr)
library(kableExtra)

#created function to make pretty tables
my_nice_table = function(your_table, vector_nice_names, nice_title){
  nice = kable(your_table, col.names = vector_nice_names, caption = nice_title)
  nice_format = kable_classic(nice, full_width = T, lightable_options = "striped", html_font = "sans-serif")
  return(nice_format)
}


```

# **Question 1**

```{r warning = FALSE, message = FALSE}
#setting up for loop
w = 10
new_data <- data.frame()

#for loop to read in the 10 drake lyrics files 
for(i in 1:w){
  file_name = paste0("drake_data_",i,".csv")
  read_data <- read.csv(file_name)
  
  new_data <- rbind(new_data, read_data)
}

#row and column count
number_of_rows <- nrow(new_data)
number_of_columns <- ncol(new_data)
```

There are 287 rows and 4 columns in this dataset. 

# **Question 2**

```{r warning = FALSE, message = FALSE}
#making all text lowercase
new_data$lyrics = str_to_lower(new_data$lyrics) 

#remove commas
new_data$lyrics = str_replace_all(new_data$lyrics, ",", "") 

#remove periods
new_data$lyrics = str_replace_all(new_data$lyrics, "\\.", "") 

#remove question marks
new_data$lyrics = str_replace_all(new_data$lyrics, "\\?", "")

#remove exclamation points
new_data$lyrics = str_replace_all(new_data$lyrics, "\\!", "") 

#remove numbers
new_data$lyrics = str_replace_all(new_data$lyrics, "[0-9]", "")

#remove new line
new_data$lyrics = str_replace_all(new_data$lyrics, "\\n", "") 
```


# **Question 3**

```{r warning = FALSE, message = FALSE}
#splits into words
split_lyrics = str_split(new_data$lyrics, " ", simplify=TRUE)

#make one long vector
split_lyrics_vec = as.vector(split_lyrics)

#remove empty elements
split_lyrics_vec = split_lyrics_vec[split_lyrics_vec != ""]

#splitting lyrics into a table with the top 20 most frequently used words 
my.table = as.data.frame(table(split_lyrics_vec))
fixed_table = arrange(my.table, desc(Freq)) [1:20,]

#making pretty table 
my_nice_table(your_table = fixed_table, vector_nice_names = c("Word", "Frequency"), nice_title = "Table of Word Frequency")
```

# **Question 4**

```{r warning = FALSE, message = FALSE}
#vector containing 8 words 
my.words = c("know", "love", "need", "think", "she", "back", "want", "time")
word_count <- data.frame()

#for loop that. counts the number of times each word appears in the lyrics
for(i in my.words){
  count = sum(str_count(new_data$lyrics, i))
  word_count = rbind(word_count, data.frame(Word = i, Count= count))
} 

#displaying the lyrics in a nice table 
my_nice_table(your_table = word_count, vector_nice_names = c("Word", "Frequency"), nice_title = "Table of Word Frequency")


#Barplot of the counts of each word
words_ggplot <- ggplot(word_count)
words_ggplot +
  geom_bar(aes(x=Word, y=Count, fill = Word), stat = "identity") + theme_minimal() +  theme(legend.position = "none") + labs(title = "Word Frequency in Lyrics", x = "Words", y = "Frequency")

```

In this instance we are shown how many times we see the word know, even if it is part of a different word like "knowing" or "knows", which is omitted in the previous question where we searched for the word "know" as a standalone and not as part of a compound word.  

# **Question 5**

```{r warning = FALSE, message = FALSE}
#restating the vector and identifying into unique albums
my.words = c("know", "love", "need", "think", "she", "back", "want", "time")
albums = unique(new_data$album)

words <- data.frame(Album = character(), word= character(), count = character())

#for loop to show how many times each word appears in each album 
for (album in albums) {
  album_data = new_data[new_data$album == album, ]
  for(i in my.words) {
    count = sum(str_count(album_data$lyrics, i))
    words = rbind(words, data.frame(Album = album, Word = i, Count= count))
  }
}

#nicely formatted table 
my_nice_table(your_table = words, vector_nice_names = c("Album","Word", "Frequency"), nice_title = "Table of Word Frequency by Album")

```


# **Question 6**

```{r warning = FALSE, message = FALSE}
#creating a for loop that shows the word counts for each album in individual plots 
for(i in my.words) {
  subset = words[words$Word == i, ]
  plot = ggplot(subset, aes(x= Album, y = Count, fill = Album)) + geom_bar(stat ="identity") + theme_minimal() +  theme(axis.text.x = element_text(angle=45, hjust =1), legend.position ="none") + labs(title = paste("Frequency of the Word:", i), x = "Album", y= "Frequency")
  print(plot)
  }

```


# **Question 7**

```{r warning = FALSE, message = FALSE}
#replace "K" and "M" with appropriate multipliers using ifelse
new_data$track_views <- ifelse(str_detect(new_data$track_views, "K"),
                                 as.numeric(str_replace(new_data$track_views, "K", "")) * 1000,
                                 as.numeric(str_replace(new_data$track_views, "M", "")) * 1000000)

#storing cleaned data in new variable 
new_data$know_count <- str_count(new_data$lyrics, "know")

#scatterplot of the count of "know" vs track views for each song
ggplot(new_data, aes(x = know_count, y = track_views, color = album)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Frequency of the Word 'Know' vs. Track Views",
       x = "Track Views",
       y = "Frequency of the Word 'Know'") 
```

There seems to be a slight negative correlation between the use of the word know and the track views; the less the word "know" is used, the more track views the track generally has.

